\begingroup
\let\cleardoublepage\relax
\let\cleardoublepage\relax

\pagebreak

\section*{Summary}

\spacedlowsmallcaps{nlp} covers many challenges.
The process of accomplishing these challenges touches on well-defined stages,
  such\,as \emph{tokenisation}, the focus of the proposal.
Current implementations on the web platform are lacking.
In part, because advanced machine learning techniques (such\,as
  \emph{supervised learning}) do not work on the web.

The audience that benefits the most from better parsing on the web platform,
  are web developers, a group which is more interested in practical use, and
  less so in theoretical applications.

The target audience's use cases for \spacedlowsmallcaps{nlp} on the web are
  vast.
Examples include automatic summarisation, sentiment recognition, spam
  detection, typographic enhancements, counting words, language recognition,
  and more.

The presented proposal is split into several smaller solutions.
These solutions come together in a proposal: \emph{Retext}, a complete
  natural language system.
\emph{Retext} takes care of parsing natural language and enables users to
  create and use plug-ins.

Parsing is delegated to \emph{parse-latin} and others, which first\,tokenise
  text into a list of words, punctuation, and white space.
Later, these tokens are parsed into a syntax tree, containing paragraphs,
  sentences, embedded content, and more. Their intellect extends several well
  known techniques.

The objects returned by \emph{parse-latin} and others are defined by
  \spacedlowsmallcaps{nlcst}.
\spacedlowsmallcaps{nlcst} defines the syntax for these objects.
\spacedlowsmallcaps{nlcst} is designed in similarity to other popular syntax
  tree specifications.

The interface to analyse and manipulate these objects is implemented by
  text\spacedlowsmallcaps{om}.
text\spacedlowsmallcaps{om} is created in similarity to other, for the
  target audience well-known, techniques.

The proposal was validated both by solving the audience's use cases with
  \emph{Retext}, and by measuring the audience's enthusiasm for \emph{Retext}.
Use cases were validated by implementing many as plug-ins for
  \emph{Retext}.
The enthusiasm showed by the target audience on social networks, through
  e-mail, and social coding was positive.

\endgroup